\chapter*{Advising}
\addcontentsline{toc}{chapter}{Advising}

When seeking answers to questions regarding courses or your degree, here is a list of some important resources. For more information, see {\fontfamily{qcr}\selectfont coe.berkeley.edu/advising}.

\section*{ESS (Engineering Student Services) Advising}

Your ESS Adviser is located in 230 Bechtel (Engineering Student Services office) and is available via appointment or drop-in advising.
Have a quick question?
Drop-in advising  is on Wednesday from 9 AM – 11:30 AM and 1 PM – 3:30 PM. For a specific time allotted exclusively to you, you are strongly encouraged to make an appointment with your ESS Adviser. Appointments are 20 minutes and you must chek-in within 5 minutes of your appointment time to avoid having to reschedule. Appointments are not on Berkeley Time (``Berkeley Time: = 10 minutes after the official start time) -- they start at the appointed time. To schedule an appointment with your adviser, go to: \newline{\fontfamily{qcr}\selectfont engineering.berkeley.edu/student-services}.

Your ESS adviser will suggest a reasonable curriculum for you to follow while Cal. This is the adviser you will want to talk to concerning requirements for your major. They also answer such questions regarding Humanities/Social Sciences (HSS) requirements, changing of majors, transfer/AP/IB credit, and engineering-related paperwork. If you are unsure of your major (or if you would like to add a major), ESS advisers are the ones to meet with.

For further questions, feel free to call or email Engineering Student Services, (510) 642-7594, or email your ESS Adviser directly. Your assigned ESS Adviser is listed by major:

\textbf{Engineering Math and Statistics (EMS), Energy Engineering (EnE) and Environmental Engineering Science (ESS)} Olivia Chan ({\fontfamily{qcr}\selectfont oychan@berkeley.edu}).

\textbf{Engineering Physics (EP):} Bryan Jones ({\fontfamily{qcr}\selectfont bkjones@berkeley.edu}).

\textbf{Engineering Undeclared (EU)} Joey Wong ({\fontfamily{qcr}\selectfont joeywong@berkeley.edu}).

\section*{Departmental Advising}

Engineering Science’s departmental advisers answer registration questions, describe courses, interpret departmental policy, and make referrals to resources on campus. They are incredible people to get to know and work with. They are dedicated to supporting you both as an Engineering Science student and as a human.

\textbf{All students should see Felicia Bautista for departmental advising.} Her office is in 750 Davis Hall and she has drop-in advising during: Mondays, Tuesday, Thursdays, and Fridays from 9 AM - Noon and 1 - 4 PM. All other times are by appointment only.


\section*{Faculty Advising}

In addition to your ESS Adviser, every Engineering Science student is assigned to one member of the faculty in their given field of study.
The Engineering Science Department assigns your faculty adviser, and you will be notified of the name of your adviser shortly after your arrival at UC Berkeley. If you develop a good relationship with your faculty adviser, they can be an invaluable resource, providing insightful, experience-based knowledge to help guide you through your years at Cal. This is the adviser you approach with specific questions regarding courses and instructors. They have a better understanding of which courses are best and most pertinent to your studies and can also provide detailed descriptions of classes. They will also approve your schedule when enrollment begins (at our Pizza with Professors event every semester) and make sure that you are meeting all of your academic requirements while maintaining good academic standing in your department.

In addition, your faculty adviser can be a friend in your department who can recommend you for research and job opportunities, as well as serving as a good source of reference for graduate school. Your faculty adviser is usually available during his or her office hours, and sometimes by appointment.

\subsection*{Energy Engineering}

Ana Claudia Arias/508 Cory Hall/{\fontfamily{qcr}\selectfont acarias@eecs.berkeley.edu}

Scott Moura/625 Davis Hall/{\fontfamily{qcr}\selectfont smoura@berkeley.edu}

Tarek Zohdi/6117 Etcheverry Hall/{\fontfamily{qcr}\selectfont zohdi@me.berkeley.edu}

Alexandra von Meier/406E Cory Hall/{\fontfamily{qcr}\selectfont vonmeier@berkeley.edu }

\subsection*{Engineering Math and Statistics}

Ilan Adler/4183 Etcheverry Hall/{\fontfamily{qcr}\selectfont adler@ieor.berkeley.edu}

James Casey/6125 Etcheverry Hall/{\fontfamily{qcr}\selectfont jcasey@me.berkeley.edu}

\subsection*{Engineering Physics}

David Attwood/567 Cory Hall/{\fontfamily{qcr}\selectfont attwood@eecs.berkeley.edu}

Junqiao Wu/322 Hearst Memorial Mining Building/{\fontfamily{qcr}\selectfont wuj@berkeley.edu}

\begin{comment}
Alex Zettl/341 Birge Hall/{\fontfamily{qcr}\selectfont azettl@physics.berkeley.edu} %on sabbatical
\end{comment}
\subsection*{Environmental Engineering Science}

Kara Nelson/663 Davis Hall/{\fontfamily{qcr}\selectfont karanelson@berkeley.edu}

\section*{Other Advising}

The College of Engineering runs a \textbf{Peer Adviser} program to assist ESS advising. The advisers are engineering upperclassmen and can help you find the right forms, answer quick questions, or chat about life. They are located in 230 Bechtel. More information at this link:

{\fontfamily{qcr}\selectfont engineering.berkeley.edu/student-services/advising/peer-advising}

The \textbf{Center for Access to Engineering Excellence (CAEE)} in 227 Bechtel Hall has two professional staff advisers and a learning support specialist available for all engineering undergraduates. There are new student programs, tutoring for introductory classes, and workshops throughout the school year. More information at this link:

{\fontfamily{qcr}\selectfont bit.ly/2boCY3j}

Often, the most reliable information and opinions come from your peers. We encourage you to \textbf{get involved in clubs} like SES so that you can network with upperclassmen and seek their advice. Additionally, clubs are generally a great source of academic resources, including academic advising sessions and peer-counseling.

\textbf{If you have questions for your Engineering Science peers, we have a Piazza page!} Piazza is a platform many college classes use to allow peers and instructors to ask, answer, and discuss questions. Create a Piazza account (with your Berkeley email) and enroll using the following link: {\fontfamily{qcr}\selectfont piazza.com/berkeley/other/engsci101}

