\chapter*{Introduction}
\addcontentsline{toc}{chapter}{Introduction}

Welcome to Cal! We, the students of the College of Engineering, would like to congratulate you on your admission to one of the finest engineering institutions in the world. You are now a member of a very elite group of students who make up Cal's Engineering Science Program.

As former freshmen and junior transfers, we understand the feelings of confusion and the overwhelming amount of information you may be experiencing as you enter UC Berkeley Engineering. It is a monumental task to sort through all of the new information and determine the path you will take here at Berkeley. You have to take the initiative to find out about classes and chart your own course. Within a couple of years, you will be making many important decisions that will undoubtedly affect your future. Drawing on our past experiences in Engineering Science and other related engineering disciplines, we hope that we will be able to give you a hand in making informed decisions and to help you avoid the pitfalls of the college system.

The Unofficial Guide to Engineering Sciences contains information concerning classes, majors, graduate schools, jobs, careers, and campus resources. We hope that this will become a valuable resource to you whenever you have any questions about the engineering program. This guide does not replace your faculty adviser, ESS adviser, or any of your peers. However, we hope that the booklet will help answer most of your questions about your new major. We also recommend you read the sections on other Engineering Science majors as well -- many students find the different perspectives helpful, and sometimes switch their focus as a result! Either way, we hope it will help you formulate your own path here at Berkeley. Welcome to the Cal Engineering family! Good luck and GO BEARS!

