\chapter*{Society of Engineering Sciences}
\addcontentsline{toc}{chapter}{Society of Engineering Sciences}

\textit{\center{The professional and social club of Engineering Science – meet others in your major!}}

\section*{Mission Statement}

The Society of Engineering Sciences is dedicated to enhancing the lives of students within the Engineering Science department at University of California, Berkeley. The Society provides a node for Engineering Science majors to meet, interact with professors and faculty advisers, find research opportunities, and explore common goals. We support the diverse interests and needs related to the interdiscipline of Engineering Science and its scholars.

Founded in 1980, the Society of Engineering Sciences is comprised of students with interests in Energy Engineering, Engineering Math and Statistics, Engineering Physics, and Environmental Engineering Science. The primary purpose of this society is to give representation to and advance the interests of the Engineering Sciences. Additionally, SES seeks to provide resources, support, and activities to Engineering Undeclared students and to represent their interests in the college. Due to our multidisciplinary nature, all majors are welcome.

SES provides the opportunity for interaction of students with common interests. While SES represents a huge diversity of fields, it also serves to unite a group of largely interdisciplinary majors, which face unique goals and issues. Overall, SES is an extremely flexible and personal organization whose main goal is to continually adapt and serve the wide variety of member interests.

Anyone interested in becoming more involved is encouraged to contact one of the officers below. Please visit our website at ses.berkeley.edu. SES is an Engineering Student Council sponsored organization.

\section*{2016-2017 SES Officers}

\begin{tabular}{lr}
  Co-President & Sinho Chewi \\
  Co-President & Vishnu Murthy \\
  Treasurer & Sean Anderson \\
  Treasurer & Camille Biscarrat \\
  Energy Engineering Representative & Kean Amidi Abraham \\
  Engineering Mathematics \& Statistics Representative & Joy Gu \\
  Engineering Physics Representative & Dennis Feng \\
  Engineering Physics Representative & Shreyas Parthasarathy \\
  Environmental Engineering Science Representative & Jordan French \\
  Event Coordinator & Kevin Qi \\
  Event Coordinator & Dennis Wang \\
  Historian & Drew Mendinueto \\
  Project Development/Social Outreach & Vania Fong \\
  Project Development/Social Outreach & Kriya Wong
\end{tabular}

